\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage[utf8]{vietnam}

\usepackage{amsthm}
% \usepackage{ntheorem}
\newtheoremstyle{theoremst}% name of the style to be used
  {\topsep}% measure of space to leave above the theorem. E.g.: 3pt
  {\topsep}% measure of space to leave below the theorem. E.g.: 3pt
  {\normalfont}% name of font to use in the body of the theorem
  {0pt}% measure of space to indent
  {\bfseries}% name of head font
  {.}% punctuation between head and body
  { }% space after theorem head; " " = normal interword space
  {\thmname{#1}\thmnumber{ #2}\textnormal{\thmnote{ (#3)}}}

\newtheoremstyle{examplest}% name of the style to be used
  {\topsep}% measure of space to leave above the theorem. E.g.: 3pt
  {\topsep}% measure of space to leave below the theorem. E.g.: 3pt
  {\normalfont}% name of font to use in the body of the theorem
  {0pt}% measure of space to indent
  {\bfseries}% name of head font
  {\\}% punctuation between head and body
  { }% space after theorem head; " " = normal interword space
  {\thmname{#1}\thmnumber{ #2}\textnormal{\thmnote{ (#3)}}}
  
\theoremstyle{theoremst}
\newtheorem{definition}{Định nghĩa}[section]
\newtheorem{theorem}{Định lý}[section]


\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}


\title{MAGNN: Metapath Aggregated Graph Neural Network for
Heterogeneous Graph Embedding\\
{\footnotesize \textsuperscript{}Giảng viên hướng dẫn: TS. Đỗ Thị Thanh Hà}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{ Nguyễn Mạnh Linh}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
\and
\IEEEauthorblockN{Nguyễn Đức Thịnh}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
}

\maketitle

\begin{abstract}
Một lượng lớn các đồ thị hay mạng trong thực tế vốn dĩ không đồng nhất, có nhiều loại nút và nhiều loại quan hệ. Embedding đồ thị không đồng nhất là việc embed từ cấu trúc lớn và nhiều thông tin của đồ thị về biểu diễn nút trong không gian thấp chiều. Các mô hình đã tồn tại tường định nghĩa metapaths trong một đồ thị không đầu nhất để ghi lại các quan hệ và định hướng lựa chọn "hàng xóm". Tuy nhiên các mô hình này bỏ qua đặc trưng của từng nút mà tìm hiểu ngay lập tức các nút trên metapath hoặc chỉ xem xét một metapath. Để khắc phục ba giới hạn này, tác giả đề xuất một mô hình mới là \textit{Metapath Aggregated
Graph Neural Network} (MAGNN) để tăng tốc hiệu năng cuối cùng. Đặc biệt, MAGNN sử dụng ba thành phần chính, biến đổi nội dung của nút thành các thuộc tính đóng gói của nút đầu vào, tổng hợp intra-metapath để kết hợp các nút ngữ nghĩa trung gian và tổng hợp inter-metapath để kết hợp thông tin từ nhiều metapaths. Các thí nghiệm được thực hiện trên ba bộ dữ liệu đồ thị không đồng nhất trong thực tế để phân loại nút, phân cụm nút và dự đoán liên kết chỉ ra rằng MAGNN đạt được kết quả dự đoán chính xác hơn so với các mô hình state-of-the-art hiện tại .
\end{abstract}

% \begin{IEEEkeywords}
% component, formatting, style, styling, insert
% \end{IEEEkeywords}

\section{Giới thiệu}
\input{sections/introduction.tex}

\section{Sơ lược}
\input{sections/preliminary.tex}

\section{Nghiên cứu liên quan}
\input{sections/related_work.tex}

\section{Phương pháp}
\input{sections/method.tex}

\section{Thực nghiệm}
\input{sections/experiments.tex}

\section{Kết luận}
\input{sections/conclusion.tex}

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}
